### 2015-11-04 CVPR16/Source/experiments.tex
Update Association Experiment and Improve Flow A Bit

\section{Experiments}
\label{sec:experiments}

In this section, we first compare our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation. We then show how the proposed model benefits the task of 3D localization in autonomous driving.

For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas. It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

We first perform the association experiment that compares the accuracy of point-to-object association using the proposed model against those of detection bounding box baseline method (BBox) and state-of-the-art motion segmentation methods, namely robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.

@@

Using our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
\begin{align}
  \assocP = \Prefl\Ptrans,
\end{align}
where $\Prefl$ and $\Ptrans$ are from \ref{eq:evalPrefl} and \ref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects. This above fraction is the association probability given the hypothesized parameters of TPs.

To compute the association probability $\assocP$ between point track $j$ and TP $i$ we must use re-projection error as well. When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution. The error terms can be converted to probability domain by considering the error term as negative log of probability
\begin{align}
  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
\end{align}

@@

We use detection bounding box based assignment of point tracks to TPs as the baseline. For the regions where the bounding boxes overlap, we assign the point tracks to the TP that has smaller mean depth than the competing bounding box.

@@

For each sequence of the KITTI dataset, the methods of \cite{} and \cite{} are used respectively for computing detection bounding boxes and object tracklets. We then apply \cite{} on object tracklets to extract point tracks. From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes). In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).

Table~\ref{tab:meanAssoc} and Figure~\ref{fig:assoc-occ-results} present the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence as well as the mean results over all sequences of the KITTI dataset. From the results, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. Both RAS and BM often have the highest errors and hence the highest mean errors on all sets of input point tracks.

\begin{figure*}
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{Association errors on different sets of point tracks. The
    numbers on y-axis represent the data sequence number in KITTI dataset. The
    first set of bars in each plot correspond to the mean across all sequences.
    The error is in terms of average fraction of foreground points incorrectly
    associated to objects per sequence.}
\label{fig:assoc-occ-results}
\end{figure*}
\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  & Ours & BBox & BM & RAS\\
  \midrule
  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 29.3 \\
  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 16.4 \\
  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{Mean association experiment results in error percentage calculated as percentage of points wrongly associated.}
\label{tab:meanAssoc}
\end{table}

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{table*}
  \centering
  \begin{tabular}{ccc}
    & Associations & Error in association\\
    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{Qualitative results for association experiment. The left column
  shows the point tracks assignment to appropriate object. Each color represents
a different track to which the point is associated to. Right column shows the
probablistic error in association: red is low error while blue is high error.
Note that our method changes smoothly at the boundary of the objects with
intermediate probabilities, while the baseline methods have only 0-1 error.} 
\end{table*}

\subsection{Localization Experiment}
To show the effectiveness of our method we apply it to the localization
problem. We estimate the position, orientation and dimensions of the car with
our framework and compute the error in birds eye view domain along the ground
plane. We report error in three metrics translation error (t) in meters per
car, yaw error (yaw) in radians per car and dimension error is again meters per
car. The results are shown in Table~\ref{tab:localizationExperiment}.

@@

\subsubsection{Continuous point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We model continuous point tracks energy with explicit occlusion reasoning as
the expected re-projection error over the association probability,

\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of
$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
and $\Ereproj(\lambda)$ is the re-projection error given by
%
\begin{align}
  \assocP &= \Prefl\Ptrans\\
  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
  \label{eq:reprojerror}
\end{align}

>>>>

\section{Experimental results}
\label{sec:experiments}

In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation. We then show how the proposed model benefits the task of 3D localization in autonomous driving. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas. It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

We first perform the association experiment that compares the accuracy of point-to-object association using the proposed model against those of the detection bounding box baseline method (BBox) and state-of-the-art motion segmentation methods, namely robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.

@@

Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ of $j$\textsuperscript{th} point track with $i$\textsuperscript{th} object at depth $\lambda$ can be defined as
\begin{align}
  \assocP = \Prefl\Ptrans,
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects. This above fraction is the association probability given the hypothesized parameters of TPs in the scene.

To compute the association probability $\assocP$ between point track $j$ and TP $i$ we must use the reprojection error as well. When the association of $i$ and $j$ is correct and the point of reflection is at depth $\lambda$, the reprojection error must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution. The error term can be converted to probability domain by considering the error term as negative log of probability
\begin{align}
  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
\end{align}

@@

For the baseline method, the associations between point tracks and TPs are achieved by using detection bounding boxes, where point tracks within each bounding box are simply assigned to it. For the regions where the bounding boxes overlap, we assign the point tracks to the TP that has smaller mean depth than the competing bounding boxes.

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used respectively for computing detection bounding boxes and object tracklets. We then apply \cite{Zach2007} on object tracklets to extract point tracks. From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes). In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).

Figure~\ref{fig:assoc-occ-results} shows the association errors --- the percentages of point tracks incorrectly assigned to objects --- of all methods on four sets of input point tracks for each sequence of the KITTI dataset, while the mean results over all sequences are presented in Table~\ref{tab:meanAssoc}. From Figure~\ref{fig:assoc-occ-results}, our method is usually the most accurate among all methods, leading to the best mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}, which is followed by the bounding box baseline method. This clearly shows the advantage of our continuous occlusion model over the simple baseline method for resolving occlusions. RAS and BM often have the highest errors in Figure~\ref{fig:assoc-occ-results}, and hence the highest mean errors on all sets of input point tracks in Table~\ref{tab:meanAssoc}.

More importantly, both RAS and BM rely on motions of objects for clustering point tracks, therefore they cannot work well with static point tracks (e.g., point tracks belong to parked cars). This fact can be observed in Table~\ref{tab:meanAssoc}, where there are large differences in the mean errors of both methods on data containing static point tracks (i.e., rows 2 and 4) and data consisting of dynamic point tracks only (i.e., rows 1 and 3). In contrast, our method and the baseline method are relatively independent of object motions, resulting in smaller performance gaps.

\begin{figure*}
\includegraphics[trim=1.0in 0.4in 1.0in 0.2in, clip, width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence.pdf}
  \caption{Association errors on different sets of input point tracks. Numbers on y-axis represent data sequence numbers in KITTI dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{fig:assoc-occ-results}
\end{figure*}
\begin{table}
\begin{tabular}{lrrrr}
  \toprule
  & Ours & BBox & BM & RAS\\
  \midrule
  Dyn. and occ. tracks        & \textbf{13.2} & 21.3 & 30.9 & 29.3 \\
  Occluded tracks             & \textbf{15.7} & 19.8 & 39.5 & 37.8 \\
  Dynamic tracks              & \textbf{06.6} & 11.4 & 15.3 & 16.4 \\
  All tracks                  & \textbf{08.6} & 12.6 & 21.9 & 21.5 \\
  \bottomrule
\end{tabular}
\caption{Mean association errors on different sets of input point tracks over all sequences of KITTI dataset. Errors are in terms of average fractions of foreground points incorrectly associated to objects per sequence.}
\label{tab:meanAssoc}
\end{table}

\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{table*}
  \centering
  \begin{tabular}{ccc}
    & Associations & Error in association\\
    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Baseline} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BM} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{Qualitative results of the association experiment. The left column
  shows the point track assignments to appropriate objects. Each color represents
a different object to which point tracks can be associated to. Right column shows the
probabilistic error in association: low errors are in red while high errors are in blue.
Note that our method changes smoothly at the object boundaries with
intermediate probabilities, while the baseline method has merely 0-1 error.} 
\end{table*}

\subsection{Localization experiment}
To show the effectiveness of our method we apply it to the localization
problem. We estimate the position, orientation and dimensions of the car with
our framework and compute the error in birds eye view domain along the ground
plane. We report error in three metrics translation error (t) in meters per
car, yaw error (yaw) in radians per car and dimension error is again meters per
car. The results are shown in Table~\ref{tab:localizationExperiment}.

@@

\subsubsection{Continuous point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}
We model continuous point tracks energy with explicit occlusion reasoning as
the expected reprojection error over the association probability,

\begin{multline}
  \Energy{track}(\{ \relp{i}{t} \}_i, \{ \relp{i}{t-1} \}_i, \{\dimsn{i}\}_i ) = 
  \\
    \sum_{i=1}^{N} 
    %\sum_{t = s_i}^{e_i}
    \sum_{j = 1}^{M}
    \int_1^\infty \assocP\Ereproj(\lambda) d\lambda
\end{multline}
where $\assocP$ is the association probability of
$j$\textsuperscript{th} point with $i$\textsuperscript{th} TP at depth $\lambda$, $\{ \relp{i}{t} \}_i$ are the poses of all occluding objects at time $t$, $ \{ \dimsn{i} \}_i$ are the dimensions of all objects that occlude $i$
and $\Ereproj(\lambda)$ is the reprojection error given by
%
\begin{align}
  \assocP &= \Prefl\Ptrans\\
  \Ereproj(\lambda) &= \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2 .
  \label{eq:reprojerror}
\end{align}

### 2015-11-04 CVPR16/Source/intro.tex
Update Association Experiment and Improve Flow A Bit

\section{Introduction}
The problem of segmenting points to objects often comes up in different
computer vision problems especially in multi-body 
reconstruction and localization. Given correspondence points on
consecutive frames, the problem becomes one of finding out which points belong
to which object following which one can use the consensus of segmented points
to reconstruct or localize the object more accurately. Without additional 
information this is very difficult problem as attempted by semantic segmentation 
and motion segmentation methods. However, in the problems like reconstruction and
localization on can use the hypothesis of the algorithm as the feedback. For

>>>>

\section{Introduction}
The problem of segmenting points to objects often comes up in different
computer vision problems especially in multi-body 
reconstruction and localization. Given correspondence points on
consecutive frames, the problem becomes one of finding out which points belong
to which object, following which one can use the consensus of segmented points
to reconstruct or localize the object more accurately. Without additional 
information, this is a very difficult problem as attempted by semantic segmentation 
and motion segmentation methods. However, in the problems like reconstruction and
localization one can use the hypothesis of the algorithm as the feedback.
% What is the problem we are trying to solve, and why is it even important?

% What did we do
We propose a novel model for representation of objects in the scene so that point tracks
can be probabilistically associated with objects while accounting for object occlusions.
% Why is it novel
Although our proposed model is inspired by Milan et
al.\cite{Milan_etal_2014}, it is more detailed and more principled than their
work. Milan et al. used soft ellipses and sigmoids to model pedestrians and
their occlusions. Our reasoning is instead in 3D. We use ellipsoids to model objects
and reason about their occupancies of the space to model their occlusions.
% Ok you proposed a model is it of any use
% How does it compare to state of art
We show that our continuous occlusion model achieves significantly lower point-to-object association errors compared to the baseline method using detection bounding boxes and other state-of-the-art methods for motion segmentation~\cite{Brox_Malik_2010, Rao_etal_2010}. As a consequence, our model benefits the task of 3D localization of traffic participants in autonomous driving.

### 2015-11-04 CVPR16/Source/setup.tex
Generated visualizations.
Update Association Experiment and Improve Flow A Bit

We are given video feed from a front facing monocular camera. We assume that features like car detections, point tracks, lane detections, ground plane and ego-motion are already available. We also use GPS and Map as a given input to the system. With this available information our goal is to find position, orientation and dimensions different participants in the scene.

We model this problem in factor graph formulation. Factor graphs are bipartite graphs containing factor node and variable nodes that describe the factorization of the joint probability over the random variables in the graph. Each factor node is connected to a variable node if and only if the corresponding function depends on the corresponding random variable node.

\begin{figure}
  \centering
  \newcommand{\imagewidth}{\textwidth}
  \input{Source/scenelayoutoverlayCity0961}
  \caption{A sample road scene with the unknowns of each car modeled as random variables. 
  The relating energies are shown in Figure~\ref{fig:graphmodel}}
\end{figure}
\begin{figure}
  %\includegraphics[width=\columnwidth]{Figures/graphicalModelFrom61ConstVars.pdf}
    %\tikzset{/tikz/x=0.8cm,/tikz/y=0.8cm}
  \begin{subfigure}[b]{0.55\textwidth}
    \input{Source/graphical_model_multiple}
    \caption{Graphical model for a single frame with state of car represented
    as single node.}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \tikzset{/tikz/x=0.8cm,/tikz/y=0.8cm}
    \include{Source/graphicalmodelTP}
    \caption{Factor graph dependence split up by pose and dimension}
  \end{subfigure}
\caption{Graphical model. The six numbered nodes represent the unknown state variables of each car. The shaded nodes in the graphical model are observed variables. %(1) Bounding box energy: The bounding box energy ($\Energy{bbox}$) without occlusion modeling is a unary term, but with occlusion it becomes a higher order term that affects the state of occluder as well. The bounding box detection is represented by $\mathbf{d}_{bb}^i(t)$. We can see that the bounding box energy affects both occluder and the occluded. (2) Point tracks energy ($\Energy{track}$) also exhibits occluder-occluded dependency.  The available point tracks are modeled by $\mathbf{u}(t)$. (3) Collision energy ($\Energy{coll}$) should ideally be globally dependent on all traffic participants but here we represent collision among only those TP that are near enough to have a significant collision energy. (4) Orientation from lane (and map) information ($\Energy{lane}$) depends only on single traffic participant hence show in the right subfigure. (5) Dynamic energies ($\Energy{dyn}$) also affect only one traffic participant at a time but over two frames. (6) Size prior ($\Energy{size}$) is used to enforce reasonable size of traffic participants.
}
  \label{fig:graphmodel}
\end{figure}
\begin{figure}
  \centering
\end{figure}

%%%%%%%%% BODY TEXT
\paragraph{The Model}

The objective is to find the most likely traffic participant (TP) state $\state{i}{t}$ given
various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \{L_m\}\}$. This problem can be formulated as to find the states that maximize the conditional probability given the evidence,
%
\begin{align}
  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})\enspace.
\end{align}
%
By applying Bayes rule we get
\begin{align}
  P(\{\state{i}{t}\} | \mathbb{E}) &=
  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\}).
\end{align}
%
Assume conditional independence according to graphical model in Figure~\ref{fig:graphmodel}, we get an equivalant factorization of the joint probability distribution
%
\begin{multline}
  P(\{\state{i}{t}\} | \mathbb{E}) =
  \frac{1}{Z}
  \prod_{t=s_i}^{e_i}
  \left(
  \prod_{i,j: i \ne j}
  P(\state{i}{t}, \state{j}{t})
  P(\bb{i} | \state{i}{t}, \state{j}{t})
  P(\trackp{t} | \state{i}{t}, \state{j}{t})
\right)
\\
\left(
  \prod_{i=1}^{N}
  P(L_m(t) | \state{i}{t})
  P(\state{i}{t} | \state{i}{t-1})
  P(\state{i}{t})
\right)
  \enspace ,
\end{multline}
where $\bb{i}$ are the car detections, $\trackp{t}$ are the point tracks, $L_m(t)$ is the lane information from lane detection or GPS and Map information.
For computational reason it is common to work on factor graphs in log domain
and for historical reasons the negative log of probability is also called the energy of the system. In energy domain our factorization simplifies to
%
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  -Z' 
  + \sum_{t=s_i}^{e_i}
  \left(
  \sum_{i,j:i\ne j}   
  \WEnergyCol 
   + \WpEnergy{bbox}
   + \WpEnergy{track}
\right)
  \\
  + \left(
  \sum_{i=1}^N 
  \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{size}
\right)
  \enspace.
\end{multline}
%
Here $\WEnergyCol = -\log P(\state{i}{t}, \state{j}{t})$ is collision energy which penalizes localization of cars that are too close together, $\WpEnergy{bbox} = -\log P(\bb{i} | \state{i}{t}, \state{j}{t})$ is bounding box energy that encourages the alignment of projected bounding box with the detected bounding box, $\WpEnergy{track} = -\log P(\trackp{t} | \state{i}{t}, \state{j}{t})$ is the point tracks energy which encourages the alignment of re-projected point tracks with ones that are detected, $\WEnergy{lane} = - \log P(L_m(t) | \state{i}{t})$ is lane energy which encourages cars to be along the direction of lanes, $\WEnergy{dyn} = - \log P( \state{i}{t} | \state{i}{t-1} ) $ is dynamic energy which captures the motion model of the cars and finally $\WEnergy{size} = - \log P (\state{i}{t})$ is the size prior over the cars. $\lambda_{\text{\{col,bbox,track,lane,dyn,size\}}}$ are unknown parameters that weight different energies. For now we set them empirically, but eventually they need to be learned from the data.

>>>>

\section{Continuous Occlusion Model}
\label{sec:setup}
The problem of segmenting points to objects often comes up in different
computer vision problems especially in multi-body 
reconstruction and localization. Given correspondence points on
consecutive frames, the problem becomes one of finding out which points belong
to which object, following which one can use the consensus of segmented points
to reconstruct or localize the object more accurately. Without additional 
information, this is a very difficult problem as attempted by semantic segmentation 
and motion segmentation methods. However, in the problems like reconstruction and
localization one can use the hypothesis of the algorithm as the feedback. For
example, in this work we use 3D localization hypotheses to fit ellipsoid
models of objects that can aid in better association of points to objects and
further leading to more accurate localization results.
